Cohort_Characteristics

### 2019-06-17 Cohort-Characteristics.Rmd
Includes both OG and ICS data

```{r load data}
DonorInfo<-read.csv("/Applications/Old Computer/Day Lab/Flow-Data/clean/ICS_Donor_Info_clean.csv")
DonorInfo<-filter(DonorInfo, SM %in% c("X", "SM"))
DonorInfo$SM<-factor(DonorInfo$SM, levels=c("X", "SM"))
DonorInfo$TB<-factor(DonorInfo$TB, levels=c("HC", "LTBI", "TB"))
DonorInfo$disease<-paste(DonorInfo$TB, DonorInfo$SM, sep="_")
DonorInfo$disease<-factor(DonorInfo$disease, levels=c("HC_X", "HC_SM",
                                                      "LTBI_X", "LTBI_SM",
                                                      "TB_X", "TB_SM"))
my_comparisons <- list(c("HC_SM", "HC_X"), c("LTBI_SM", "LTBI_X"), c("TB_SM", "TB_X"), 
                       c("HC_SM", "LTBI_SM"), c("TB_SM", "LTBI_SM"), c("HC_SM", "TB_SM"),
                       c("HC_X", "LTBI_X"), c("TB_X", "LTBI_X"), c("HC_X", "TB_X"))
DonorInfo$SchistosomaIntensity[DonorInfo$SM=="X"]<-NA
```

@@

#Total Population
table1 <- CreateTableOne(vars = listVars, data = DonorInfo, factorVars = catVars,
                         strata = c("TB", "SM"))
test<- print(table1, showAllLevels = TRUE, nonnormal = mediqr, quote = FALSE, noSpaces = TRUE,
             printToggle = FALSE)

@@

library(compareGroups)
res.total<-descrTable(~ age + sex + QFT + SchistosomaIntensity, data = DonorInfo)
res <- compareGroups(SM ~ age + sex + QFT + SchistosomaIntensity, data = DonorInfo, 
                     method = c(age = 2, QFT = 2, SchistosomaIntensity = 2, sex = 3))

restab <- createTable(res, type = 1, hide.no = "no", show.n = FALSE)
test<-strataTable(restab, "TB")
export2md(test, header.labels = c(p.overall = "p-value"))
export2md(res.total)

@@

Plotting stuff against age and sex
```{r age and sex vs, cache = TRUE}
compass<-read.csv("/Applications/Old Computer/Day Lab/Flow-Data/clean/ICS_Compass_scores_complete.csv")
CD4<-read.csv("/Applications/Old Computer/Day Lab/Flow-Data/clean/CD4_clean.csv")
CD4_cyt<-read.csv("/Applications/Old Computer/Day Lab/Flow-Data/clean/CD4_Cytokine_clean.csv")

>>>>

```{r load data}
DonorInfo<-read.csv("/Applications/Old Computer/Day Lab/Flow-Data/clean/DonorInfo_clean.csv")
DonorInfo<-filter(DonorInfo, SM %in% c("X", "SM"))
DonorInfo$SM<-factor(DonorInfo$SM, levels=c("X", "SM"))
DonorInfo$TB<-factor(DonorInfo$TB, levels=c("HC", "LTBI", "TB"))
DonorInfo$disease<-paste(DonorInfo$TB, DonorInfo$SM, sep="_")
DonorInfo$disease<-factor(DonorInfo$disease, levels=c("HC_X", "HC_SM",
                                                      "LTBI_X", "LTBI_SM",
                                                      "TB_X", "TB_SM"))
my_comparisons <- list(c("HC_SM", "HC_X"), c("LTBI_SM", "LTBI_X"), c("TB_SM", "TB_X"), 
                       c("HC_SM", "LTBI_SM"), c("TB_SM", "LTBI_SM"), c("HC_SM", "TB_SM"),
                       c("HC_X", "LTBI_X"), c("TB_X", "LTBI_X"), c("HC_X", "TB_X"))
DonorInfo$SchistosomaIntensity[DonorInfo$SM=="X"]<-NA

@@

#Total Population
table1 <- CreateTableOne(vars = listVars, data = DonorInfo, factorVars = catVars,
                         strata = c("TB", "SM"))
test<- print(table1, showAllLevels = TRUE, nonnormal = mediqr, quote = FALSE, noSpaces = TRUE, printToggle = FALSE, na.print=FALSE)

@@

library(compareGroups)
res.total<-descrTable(~ age + sex + QFT + SchistosomaIntensity, data = DonorInfo, na.action = na.exclude)

res <- compareGroups(SM ~ age + sex + QFT + SchistosomaIntensity, data = DonorInfo,
    method = c(age = 2, QFT = 2, SchistosomaIntensity = 2, sex = 3))

restab <- createTable(res, type = 1, hide.no = "no", show.n = FALSE,
                      show.p.overall = TRUE, show.p.mul = TRUE,
                      q.type=c(2,3))
test<-strataTable(restab, "TB")
export2md(test, header.labels = c(p.overall = "p-value"))
export2md(res.total)

@@

Plotting stuff against age and sex
```{r age and sex vs, cache = TRUE, eval=FALSE}
compass<-read.csv("/Applications/Old Computer/Day Lab/Flow-Data/clean/ICS_Compass_scores_complete.csv")
CD4<-read.csv("/Applications/Old Computer/Day Lab/Flow-Data/clean/CD4_clean.csv")
CD4_cyt<-read.csv("/Applications/Old Computer/Day Lab/Flow-Data/clean/CD4_Cytokine_clean.csv")
